Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-12 paper/AlignedIsotropicGW.tex
Added Gerosa & B. Farr to acknowledgments
Ben moves from acknowledgements to co-author.

@@

\email{w.farr@bham.ac.uk, simons@star.sr.bham.ac.uk, miller@astro.umd.edu,\\imandel@star.sr.bham.ac.uk, av@star.sr.bham.ac.uk}

@@

We thank Richard O'Shaughnessy and Christopher Berry for discussions and
comments on this work.  WF, SS, IM and AV were supported in part by the STFC.  MCM acknowledges support of the University of
Birmingham Institute for Advanced Study Distinguished Visiting Fellows
program.   SS and IM acknowledge support from the National Science Foundation under Grant No. NSF PHY11-25915.

>>>>

\author[0000-0002-2916-9200]{Ben Farr}

\affiliation{Enrico Fermi Institute, University of Chicago, Chicago, IL 60637, USA}

@@

\email{w.farr@bham.ac.uk, simons@star.sr.bham.ac.uk, miller@astro.umd.edu,\\imandel@star.sr.bham.ac.uk, farr@uchicago.edu, av@star.sr.bham.ac.uk}

@@

We thank Richard O'Shaughnessy, Christopher Berry, and Davide Gerosa
for discussions and comments on this work.  WF, SS, IM and AV were
supported in part by the STFC.  MCM acknowledges support of the
University of Birmingham Institute for Advanced Study Distinguished
Visiting Fellows program.  SS and IM acknowledge support from the
National Science Foundation under Grant No. NSF PHY11-25915.
